One page description

### 2016-09-30 publications/Journal/3-features.tex
Further review of style, acronyms.
Signed-off-by: Ben Cardoen <bencardoen@gmail.com>

An overview of \textit{dxex}'s design is given in Figure~\ref{fig:class_diagram}.
It shows that there is a simulation \texttt{Core}, which simulates the \texttt{AtomicModel}s connected to it.
The superclass \texttt{Core} represents the sequential simulation core.
Subclasses define specific variants, such as \texttt{ConservativeCore} (conservative synchronization), \texttt{OptimisticCore} (optimistic synchronization), and \texttt{DynamicCore} (\textsf{Dynamic Structure DEVS}).

@@

\subsubsection{Random Number Generators}
Random Number Generators (RNG) are another aspect of the program that can limit parallelization.
All accesses to the RNG will result in the modification of a global (\textit{i.e.}, shared between threads) variable.
This easily becomes a bottleneck in simulation, since random numbers are a common occurence in simulation~\cite{Random}.
As such, a non-trivial amount of time in a simulation is often spent waiting for an RNG.

>>>>

An overview of \textit{dxex}'s design is given in Figure~\ref{fig:class_diagram}.
It shows that there is a simulation \texttt{Core}, which simulates the \texttt{AtomicModel}s connected to it.
The superclass \texttt{Core} represents the sequential simulation kernel.
Subclasses define specific variants, such as \texttt{ConservativeCore} (conservative synchronization), \texttt{OptimisticCore} (optimistic synchronization), and \texttt{DynamicCore} (\textsf{Dynamic Structure DEVS}).

@@

\subsubsection{Random Number Generators}
Random Number Generators (RNG) are another aspect of the program that can limit parallelization.
All accesses to the RNG will result in the modification of a global (\textit{i.e.}, shared between threads) variable.
This easily becomes a bottleneck in simulation, since random numbers are a common occurence in simulation~\cite{Random}.
As such, a nontrivial amount of time in a simulation is often spent waiting for an RNG.

### 2016-09-30 publications/Journal/5-hotswap.tex
Further review of style, acronyms.
Signed-off-by: Ben Cardoen <bencardoen@gmail.com>

We add performance metrics in the simulation kernel, which logs relevant performance metrics and processes them for use in other components.
These metrics include the number of events created and destroyed, the number of inter- and intra-kernel events, the number of rollbacks, the measured lookahead, details of the Global Virtual Time (GVT) and Earliest Output Time (EOT) calculations, and information on the fairness between simulation kernels.
With all these metrics, a component can get a fair view on both model and simulation kernel behaviour.

>>>>

We add performance metrics in the simulation kernel, which logs relevant performance metrics and processes them for use in other components.
These metrics include the number of events created and destroyed, the number of inter- and intra-kernel events, the number of rollbacks, the measured lookahead, details of the GVT and EOT calculations, and information on the fairness between simulation kernels.
With all these metrics, a component can get a fair view on both model and simulation kernel behaviour.

### 2016-09-30 publications/Journal/conclusion.tex
Further review of style, acronyms.
Signed-off-by: Ben Cardoen <bencardoen@gmail.com>

First, although one of both synchronization protocols might be ideally suited for specific model behaviour, nothing guarantees that the model will exhibit the same behaviour throughout the simulation.
Similarly to the polymorphic scheduler~\cite{MasterThesis}, we wish to make it possible for the ideal option to be switched during simulation.
When changes to the model behaviour are noticed, the used synchronization protocol is modified as well.

Second, the allocation of models is tricky and has a significant impact on performance.
While our parallel speedup for the Queue model, for example, was rather high, this is mostly due to characteristics of the model: the dependency graph does not contain any cycles.
When cycles were introduced, as in the Interconnect model, performance became disastrous.

>>>>

First, although one of both synchronization protocols might be ideally suited for specific model behaviour, nothing guarantees that the model will exhibit the same behaviour throughout the simulation.
Similarly to the polymorphic scheduler~\cite{MasterThesis}, we wish to make it possible for the ideal option to be switched during simulation.
When changes to the model behaviour are noticed, the used synchronization protocol can be switched as well.

Second, the allocation of models is nontrivial and has a significant impact on performance.
While our parallel speedup for the Queue model, for example, was rather high, this is mostly due to characteristics of the model: the dependency graph does not contain any cycles.
When cycles were introduced, as in the Interconnect model, performance became disastrous.
